Community-Conditioned Language Models

### 2021-05-04 paper/paper.tex
new outline

\begin{document}
\maketitle
\begin{abstract}
  Community-Conditioned Language Models (CCLMs) are an under-researched tool for 
  investigating community-level linguistic variation.
  In this paper, we experiment with different neural CCLM architectures and
  report empirical results from CCLMs trained on 510 online communities.
  We find that the community embeddings learned by these models
  correlate with representations based on non-linguistic features.
  We define a metric of the linguistic \emph{indiscernability} of a community
  and investigate the relationship between indiscernibility and other
  linguistic properties of the community.
\end{abstract}

@@

%\jp{Perhaps: Outline of the paper.}

>>>>

\begin{document}
\maketitle
\begin{abstract}
  % Context (Optional)

  % Problem?

  - Can community-level linguistic variation be captured by statistical models?

  - Is community-specific linguistic variation correlated with social
    relationship between communities?

  % Why it's interesting

  % Results

  % What follows from results? (Optional)

  Community-Conditioned Language Models (CCLMs) are an under-researched tool for 
  investigating community-level linguistic variation.
  In this paper, we experiment with different neural CCLM architectures and
  report empirical results from CCLMs trained on 510 online communities.
  We find that the community embeddings learned by these models
  correlate with representations based on non-linguistic features.
  We define a metric of the linguistic \emph{indiscernability} of a community
  and investigate the relationship between indiscernibility and other
  linguistic properties of the community.
\end{abstract}

% Introduction

% Data sets

% Community Conditioned Language Models:
%   Architecture (with emphasis on the embeddings)
%   Training
%   Results (loss and loss per community)

% Latent bayesian community classifier
%    Formula (no training!)
%    Result 1: Confusion matrix
%    Transition: too much data; can we extract a more useful metric?
%    Indiscernibility: Formula, and table

% Correlation between linguistic embedding with social embeddings
%    Explain the problem (idea: comparing cosine similarities --> too much data, again)
%    Sketch "procrustes" problem, explain what it yields. (Also what kind of similarity one gets with random input)
%    Results:
%      - Correlation between Kumar2018 and best LSTM
%      - Correlation between Kumar2018 and best Transformer 
%      - Correlation between Transformer and LSTM
%      - Concatenations ???

@@
